Project Setup

### 2024-11-28 setup.qmd
Add total number of software citation principles
Mention CC BY 4.0 license for software citation principles

If you rely on software or data by others in your research, the question arises whether and how to cite it in your publications. Put simply, all data relied upon should be cited to allow for precise identification and access. From the "eight core principles of data citation" [@Starr2015, licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/)]:

@@

When it comes to software, the answer is a little more nuanced – you can consult @fig-software-citation for advice whether to cite it. As with data, citations should allow for exact identification and access. From the "software citation principles" [@Smith2016]:

@@

To help with generating the citation, you can use the [CiteAs](https://citeas.org/) service.

>>>>

If you rely on software or data by others in your research, the question arises whether and how to cite it in your publications. Put simply, all data relied upon should be cited to allow for precise identification and access. From the "eight core principles of data citation" by @Starr2015, licensed under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/):

@@

When it comes to software, the answer is a little more nuanced – you can consult @fig-software-citation for advice whether to cite it. As with data, citations should allow for exact identification and access. From the six "software citation principles" by @Smith2016, licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/):

@@

To help with generating the citation, you can use the [CiteAs service](https://citeas.org/).
